External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-08 CVPR2017_Review_Unified.tex
ad

%Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images. The camera sensors and outdoor low light conditions will unavoidably bring noise to the captured images. The impact is that the image details will be lost or hardly visible. As a result,

Image denoising is an essential procedure for the reliability of many vision systems such as medical imaging and surveillance. It is also an ideal platform for testing computer vision models. Image denoising is to recover the latent clean image $\mathbf{x}$ from its noisy observation $\mathbf{y}=\mathbf{x}+\mathbf{n}$ where $\mathbf{n}$ is the additive noise. For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,ncsr,wnnm,csf,pgpd,chen2015learning}, and most of them focus on additive white Gaussian noise (AWGN). These methods exploited self-similarity \cite{nlm,epll,wnnm,pgpd}, structural sparsity \cite{ksvd,bm3d,cbm3d,lssc,ncsr}, neural network \cite{mlp}, or learned filters \cite{foe,csf,chen2015learning} for image denoising problem.

However, in real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc. Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}. Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}. It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc.). The models designed for AWGN would become much less effective on real noisy images.

In the last decade, the methods of \cite{crosschannel2016,fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR} are developed to deal with real noisy images. Almost all these methods employ a two-stage framework: estimating the parameters of the assumed noise model (usually Gaussian) and performing denoising with the help of the noise modeling and estimation in the first stage. However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}. Although the mixture of Gaussians (MoG) model is possible to approximate any noise distribution \cite{Bishop}, estimating its parameters is time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR}. To evaluate the performance of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}. The testing image is captured by a Nikon D800 camera when ISO is 3200. The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR. The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or over-smooth the complex details in real noisy image. 
\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 33.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}: 35.39dB }
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning}: 35.97dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) NC \cite{noiseclinic}: 35.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) NI \cite{neatimage}: 34.39dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours: \textbf{37.02}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the real noisy image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\vspace{-3mm}
\label{fig1}
\end{figure*}

The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising. The external priors in natural images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and priors of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images. Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising. The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. Both of the two stages have closed-form solutions. Hence, our internal DL process is very efficient for online internal denoising. Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising.

\subsection{Our Contributions}

The contributions of this paper are summarized as follows:
\begin{itemize}
\item We propose a novel model to learn internal priors adaptive to given images. This model employs the external patch group (PG) prior learned from clean images to guide the internal PG prior learning of given images. The external prior benefits the internal learning on subspace selection and orthogonal dictionary learning.
\item The proposed guided internal prior learning method is very efficient. The reason is that both the subspace selection and orthogonal dictionary learning have explicit solutions.
\item For real image denoising problem, the proposed method achieves much better performance than other competing methods.
\end{itemize}

>>>>

Image denoising is an ideal platform for testing computer vision models and an essential procedure for the reliability of many vision systems such as medical imaging and surveillance. It aims to recover the latent clean image $\mathbf{x}$ from its noisy observation $\mathbf{y}=\mathbf{x}+\mathbf{n}$ where $\mathbf{n}$ is the additive noise. For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,ncsr,wnnm,csf,pgpd,chen2015learning} most of which focusing on additive white Gaussian noise (AWGN). These methods exploited self-similarity \cite{nlm,epll,wnnm,pgpd}, structural sparsity \cite{ksvd,bm3d,cbm3d,lssc,ncsr}, neural network \cite{mlp}, or learned filters \cite{foe,csf,chen2015learning} for image denoising problem.

However, the methods designed for synthetic Gaussian noise is much less effective for removing the noise in real noisy images. The reason is that the noise in real noisy images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.). Besides, by the seminar work of \cite{healey1994radiometric}, the noise in the camera imaging process \cite{NewInCamera,crosschannel2016} are signal dependent and identified by five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise. This would largely limit the performance of these methods, which are designed for signal independent noise, on dealing with complex real noise. To prove our argument, we apply some representing methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning} on a real noisy image provided in \cite{crosschannel2016}. The testing image is captured by a Nikon D800 camera when ISO is 3200. The ``ground truth" image is also provided with which we can calculate objective measurements such as PSNR. The denoised images of these methods are listed in Figure \ref{fig1} (from (b)$\sim$(f)). One can see that these methods either remove the noise or over-smooth the complex details in real noisy image.

In the last decade, there are also several methods \cite{crosschannel2016,fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR} developed for real noisy image denoising. Almost all these methods employ a two-stage framework: firstly estimating the parameters of the assumed noise model (usually Gaussian distribution or mixture of Gaussians (MoG)) and then performing denoising with the help of the estimated noise model. However, the noise in real noisy images are very complex and hard to be modeled by explict distributions. Therefore, the denoising performance of these methods would be influenced by the error between the estimated noise model and the actual noise distribution. This can be validated by the   denoised results listed in Figure \ref{fig1} ((g) and (h)), in which we evaluate the state-of-the-art real noisy image denoising method Noise Clinic \cite{noiseclinic,ncwebsite} and a comercial denoising software Neat Image \cite{neatimage}. From the results, we can see that the two methods do not perform well on the testing noisy image. These methods only exploit internal priors (e.g., noise prior, self-similarity) for real noisy image denoising and ignore the information of external natural clean images. 
\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 33.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}: 35.39dB }
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning}: 35.97dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) NC \cite{noiseclinic}: 35.33dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) NI \cite{neatimage}: 34.39dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours: \textbf{37.02}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}\vspace{-1mm}
\caption{Denoised images of the real noisy image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\vspace{-3mm}
\label{fig1}
\end{figure*}

The external priors in natural images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and priors of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images. In this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising. The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. Both of the two stages have closed-form solutions. Hence, our internal DL process is very efficient for online internal denoising. Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising.

%The contributions of this paper are summarized as follows:
%\begin{itemize}
%\item We propose a novel model to learn internal priors adaptive to given images. %This model employs the external patch group (PG) prior learned from clean images to guide the internal PG prior learning of given images. The external prior benefits the internal learning on subspace selection and orthogonal dictionary learning.
%\item The proposed guided internal prior learning method is very efficient. The reason is that both the subspace selection and orthogonal dictionary learning have explicit solutions.
%\item For real image denoising problem, the proposed method achieves much better performance than other competing methods.
%\end{itemize}
